### 2023-03-11 doc/example.tex
Update docs

LitREPL for latex recognizes \texttt{lcode} environments as code and
\texttt{lresult} as result sections. The tag names is currently hardcoded into
the simple parser the tool is using, so we need to additionally introduce it to
the Latex system. Here we do it in a most simple way.

@@

Executable section is the text between the \texttt{lcode} begin/end tags.
Putting the cursor on it and typing the \texttt{:LitEval1} executes it in the
background Python interpreter.

@@

\texttt{lresult} tags next to the executable section mark the result section.
The output of the executable section will be pasted here. The
original content of the section will be replaced.

@@

Commented \texttt{lresult}/\texttt{lnoresult} tags also marks result sections.
This way we could customise the Latex markup for every particular section.

\begin{lcode}
print("Hi!")
\end{lcode}

@@

Additionally, VimREPL for Latex recognises \texttt{linline} tags for which it
prints its first argument and pastes the result in place of the second argument.

>>>>

LitREPL treats \texttt{lcode} environment as code sections and \texttt{lresult}
environment as result sections. The names are currently hardcoded into the
simplified LitREPL parser. Wrapping it in other tags is not allowed.

LaTeX does not know anything about these environments by default, we need to
introduce them to be able to compile the document using e.g. \texttt{pdflatex}.

@@

Executable section is the text between the \texttt{lcode} begin/end tags.

@@

Putting the cursor on it and typing the \texttt{:LitEval1} runs the code in the
background Python interpreter.

\texttt{lresult} begin/end tags mark the result section.  LitREPL replaces its
content with the above code section's execution result.

@@

LitREPL recognizes \texttt{l[no]code}/\texttt{l[no]result} comments as
code/result section markers. This way we can use Python to produce LaTeX markup
as output.

%lcode
print("Hi!")
%lnocode

@@

Additionally, VimREPL recognises \texttt{linline} 2-argument tags. The first
arguement is treaten as a Python printable expression. The second arguemnt is to
be replaced with the printing output. In our simplified definition, we simply
ignore the first argument and paste the second to the LaTeX processor as-is.
